Modeling HEPES buffer with a charge-balance approach

### 2023-11-17 manuscript.Rmd
Illustrate Vectorize()

**IK**: This feels like I'm writing a tutorial. Should I be less
detailed?

@@

```{r HEPESFUNC}
HEPESFUNC <- function(H,SID,HEPTOT,pK1,pK2,pK3) {
	XX <- (H^3/(10^-pK3*10^-pK2*10^-pK1)+H^2/(10^-pK3*10^-pK2)+H/(10^-pK3))
	IV <- HEPTOT/(1+XX)
	I <- IV*H^3/(10^-pK3*10^-pK2*10^-pK1)
	II <- IV*H^2/(10^-pK3*10^-pK2)
	III <- IV*H/10^-pK3
	H - kw/H + SID + I*2 + II - IV
}
```

@@

The base function `Vectorize` automates this transformation. It returns
a wrapper function that obtains the values of every argument given to
the wrapper and passes them to a live-constructed call to `mapply()`,
letting the latter call the original function. A call to
`mapply(f, a, b, c)`, returns a vector of values of
`f(a[i], b[i], c[i])` for every applicable `i`, subject to vector
recycling rules.

>>>>

**IK**: This feels like I'm writing a tutorial. Should it be less
detailed?

@@

```{r HEPESFUNC}
kw <- 1e-14
HEPESFUNC <- function(H,SID,HEPTOT,pK1,pK2,pK3) {
	XX <- (H^3/(10^-pK3*10^-pK2*10^-pK1)+H^2/(10^-pK3*10^-pK2)+H/(10^-pK3))
	IV <- HEPTOT/(1+XX)
	I <- IV*H^3/(10^-pK3*10^-pK2*10^-pK1)
	II <- IV*H^2/(10^-pK3*10^-pK2)
	III <- IV*H/10^-pK3
	H - kw/H + SID + I*2 + II - IV
}
```

@@

The base function `Vectorize` automates this transformation. It returns
a wrapper function that obtains the values of every argument given to
the wrapper and passes them to a live-constructed call to `mapply()`,
letting the latter call the original function. A call to
`mapply(f, a, b, c)`, returns a vector of values of
`f(a[i], b[i], c[i])` for every applicable `i`, subject to vector
recycling rules:

```{r}
pHm <- Vectorize(pH)
ans <- c(
 pH(.04, .05, -1, 3, 7.55),
 pH(.035, .05, -1, 3, 7.55)
)
all.equal(ans, pH.wrapper(
 c(.04, .035), .05, -1, 3, 7.55
))
all.equal(ans, pHm(
 c(.04, .035), .05, -1, 3, 7.55
))
```
